Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-27 review_article.Rmd
plot updates for sizing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(png)
library(grid)
```
<!--

@@

```{r choroCRS, fig.cap = "Four choropleth maps of the United States of America using various coordinate reference systems. Each state has been colored according to the average age-adjusted rate of incidence for lung and bronchus for females and males in the United States 2012-2016. The map projections alter the shapes and angles of the boundaries of each state. Maps a and b are similar in their straight edges, unlike maps c and d which curve on the northern United States border.", message=FALSE, warning=FALSE, out.width='100%', fig.align='center', fig.width=12}
knitr::include_graphics("figures/ggchoroCRS.png")
```

@@

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(g1), 0, .5, 0.5, 0.55) +
  draw_plot(rasterGrob(g2), 0.5, 0.5, 0.5, 0.55) +
  draw_plot(rasterGrob(g3), 0.0, 0.0, 0.5, 0.55) +
  draw_plot(rasterGrob(g4), 0.5, 0, 0.5, 0.55) +
  draw_plot(usa_legend, 0, 0, 1, 0.1) +
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(cowplot)
library(png)
library(grid)
```
<!--

@@

```{r choroCRS, fig.cap = "Four choropleth maps of the United States of America using various coordinate reference systems. Each state has been colored according to the average age-adjusted rate of incidence for lung and bronchus for females and males in the United States 2012-2016. The map projections alter the shapes and angles of the boundaries of each state. Maps a and b are similar in their straight edges, unlike maps c and d which curve on the northern United States border.", message=FALSE, warning=FALSE, out.width='100%', fig.align='center'}
#knitr::include_graphics("figures/ggchoroCRS.png")
c1 <- png::readPNG("figures/gg3857.png")
c2 <- png::readPNG("figures/gg2163.png")
c3 <- png::readPNG("figures/gg4326.png")
c4 <- png::readPNG("figures/gg2955.png")
#knitr::include_graphics("figures/usa_grid.png")
load("figures/usa_legend.rda")

ggdraw() +
  draw_plot(rasterGrob(c1), 0, .55, 0.5,    0.45) +
  draw_plot(rasterGrob(c2), 0.5, 0.55, 0.5, 0.45) +
  draw_plot(rasterGrob(c3), 0.0, 0.1, 0.5, 0.45) +
  draw_plot(rasterGrob(c4), 0.5, 0.1, 0.5,   0.45) +
  draw_plot(usa_legend, 0, 0, 1, 0.1, scale = 2) +
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```

@@

ggdraw() +
  draw_plot(rasterGrob(g1), 0, .55, 0.5,  0.45) +
  draw_plot(rasterGrob(g2), 0.5, 0.55, 0.5, 0.45) +
  draw_plot(rasterGrob(g3), 0.0, 0.1, 0.5, 0.45) +
  draw_plot(rasterGrob(g4), 0.5, 0.1, 0.5, 0.45) +
  draw_plot(usa_legend, 0, 0, 1, 0.1, scale = 2) +
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```
